\section{Introduction}
\label{sec:intro}

The Deep Underground Neutrino Experiment (DUNE)~\cite{Abi:2020wmh} is a next-generation long-baseline neutrino oscillation experiment which will utilize high-intensity \numu and \anumu beams with peak neutrino energies of $\approx$2.5~GeV over a 1285 km baseline to carry out a detailed study of neutrino mixing. Some of DUNE's key scientific goals are the definitive determination of the neutrino mass ordering, the definitive observation of charge-parity symmetry violation (CPV) for more than 50\% of possible true values of the charge-parity violating phase, \deltacp, and the precise measurement of other three-neutrino oscillation parameters.
These measurements will help guide theory in understanding if there are new symmetries in the neutrino sector and whether there is a relationship between the generational structure of quarks and leptons~\cite{Qian:2015waa}. Observation of CPV in neutrinos would be an important step in understanding the origin of the baryon asymmetry of the universe~\cite{Fukugita:1986hr, Davidson:2008bu}. DUNE has a rich physics program beyond the three-neutrino oscillation accelerator neutrino program described here. These include beyond standard model searches~\cite{Abi:2020kei}, supernova neutrino detection~\cite{Abi:2020lpk}, and solar neutrino detection~\cite{Capozzi:2018dat}. Additional physics possibilities with DUNE are discussed in Refs.~\cite{Abi:2020evt} and~\cite{AbedAbud:2021hpb}.

Neutrino oscillation experiments have so far measured five of the three-neutrino mixing parameters~\cite{Capozzi:2017ipn,deSalas:2020pgw,Esteban:2020cvm}: the three mixing angles $\theta_{12}$, $\theta_{23}$, and $\theta_{13}$; and the two squared-mass differences $\Delta m^{2}_{21}$ and $|\Delta m^{2}_{31}|$, where $\Delta m^2_{ij} = m^2_{i} - m^{2}_{j}$ is the difference between the squares of the neutrino masses.
The neutrino mass ordering (the sign of $\Delta m^{2}_{31}$) is not currently known, though recent results show a weak preference for the normal ordering (NO), where $\Delta m^{2}_{31} > 0$, over the inverted ordering (IO)~\cite{Abe:2021gky,PhysRevD.97.072001,PhysRevLett.123.151803}.
The value of \deltacp is not well known, though neutrino oscillation data are beginning to provide some information on its value~\cite{Abe:2019vii,Abe:2021gky}.

The oscillation probability of $\;\nu^{\bracketbar}_\mu \rightarrow \nu^{\bracketbar}_e$ through matter in the standard three-flavor model and a constant matter density approximation can be written as~\cite{Nunokawa:2007qh}:
\begin{linenomath*}
  \begin{equation}
    \begin{aligned}
      P(\;\nu^{\bracketbar}_\mu \rightarrow \nu^{\bracketbar}_e) & \simeq \sin^2 \theta_{23} \sin^2 2 \theta_{13} 
      \frac{ \sin^2(\Delta_{31} - aL)}{(\Delta_{31}-aL)^2} \Delta_{31}^2 \\
      & + \sin 2 \theta_{23} \sin 2 \theta_{13} \sin 2 \theta_{12}\frac{ \sin(\Delta_{31} - aL)}{(\Delta_{31}-aL)} \Delta_{31} \\
      &\times \frac{\sin(aL)}{(aL)} \Delta_{21} \cos (\Delta_{31} \pm \deltacp) & \\
      & + \cos^2 \theta_{23} \sin^2 2 \theta_{12} \frac {\sin^2(aL)}{(aL)^2} \Delta_{21}^2,
    \end{aligned}
    \label{eqn:appprob}
  \end{equation}
\end{linenomath*}
where
\begin{linenomath*}
  \begin{equation*}
    a = \pm \frac{G_{\mathrm{F}}N_e}{\sqrt{2}} \approx \pm\frac{1}{3500~\mathrm{km}}\left(\frac{\rho}{3.0~\mathrm{g/cm}^{3}}\right),
  \end{equation*}
\end{linenomath*}
$aL \approx 0.367$, $G_{\mathrm{F}}$ is the Fermi constant, $N_e$ is the number density of electrons in the Earth's crust, $\Delta_{ij} = 1.267 \Delta m^2_{ij} L/E_\nu$, $\Delta m^2_{ij}$ is in eV$^{2}$, $L$ is the baseline in km, and $E_\nu$ is the neutrino energy in GeV.
Both \deltacp and $a$ terms are positive (negative) for $\numu \to \nue$ ($\anumu \to \anue$) oscillations. The matter effect asymmetry encapsulated in the $a$ terms arises from the presence of electrons and absence of positrons in the Earth's crust~\cite{Wolfenstein:1977ue,Mikheev:1986gs}. In the analysis described here, the oscillation probabilities are calculated exactly~\cite{Kopp:2006wp}.

DUNE has published sensitivity estimates~\cite{Abi:2020qib} to CPV and the neutrino mass ordering, as well as other oscillation parameters, for large exposures of up to 1104 kiloton-megawatt-years (kt-MW-yr), which show the ultimate sensitivity of the experiment. Sophisticated studies with a detailed treatment of systematic uncertainties were carried out only at large exposures. In this work, DUNE's sensitivity at low exposures is explored further, with a detailed systematics treatment, including an investigation into how the run plan may be optimized to enhance sensitivity to CPV and/or mass ordering. It is shown that DUNE will produce world-leading results at relatively short exposures, which highlights the need for a high-performance near detector complex from the beginning of the experiment. 

The DUNE far detector (FD) will ultimately consist of four modules, each with a 17 kt total mass. The neutrino beam-line has an initial design intensity of 1.2 MW, with a planned upgrade to 2.4 MW. We assume a combined yearly Fermilab accelerator and neutrino beam-line uptime of 57\%~\cite{Abi:2020evt}, and include this in our calculation of calendar years in this work. As the FD deployment schedule and beam power scenarios are both subject to change, the results shown in this work are consistently given in terms of exposure in units of kt-MW-yr, which is agnostic to the exact staging scenario, but can easily be expressed in terms of experiment years for any desired scenario. For example, with two FD modules, assuming a fiducial mass of 10 kt and a beam intensity of 1.2 MW, exposure would accumulate at a rate of 24 kt-MW-yr per calendar year, although a ramp up in beam power is expected before reaching the design intensity in early running. In this work, the single-phase horizontal drift technology is assumed for all FD modules (see Section~\ref{sec:fd}), which is a necessary simplification, but alternative technologies which may have slightly different performance are under investigation for some FD modules.

The analysis framework is described in Section~\ref{sec:analysis_framework}, including a description of the flux, neutrino interaction and detector models and associated uncertainties. A study of the dependence of the sensitivity to CPV and mass ordering on the fraction of data collected in neutrino-enhanced or antineutrino-enhanced running is given in Section~\ref{sec:run_plan_opt}. A detailed study of the CPV and mass ordering sensitivities at low exposures are described in Sections~\ref{sec:cp_sens} and~\ref{sec:mh_sens}, respectively. Finally, conclusions are presented in Section~\ref{sec:conclude}.

